\section*{Today goals}
\begin{itemize}
	\item Decide one and for once which domains to blacklist and provide
        VenueIdCrawler with an initial mapping of url to id based on a small
        sample.
    \item Then run four hours on \texttt{xaa}, maybe update the blacklist and
        save the resulting mapping.
    \item Finally, join \texttt{xab-j} and run it for a few days.
	\item Scrap venue webpage to get recommended venues, which can be use as a
        baseline validation (or look for a programmatic way of doing it)
	\item Prepare requests to build time activity of venues
    \item Look at Twitter
        \href{https://dev.twitter.com/docs/streaming-apis/streams/public}{public
        stream API} to collect more check in. Ask MM id there is code available
    \item Build a mapping from (lat, lng) to venue id and use it to improve
        checkin without venue id.
	\item Draw a Flickr Helsinki heatmap with leaflet.
\end{itemize}

\section*{Today results}
\begin{itemize}
    \item blacklist: done
    \item similar: There is
        \texttt{\href{https://developer.foursquare.com/docs/venues/similar}{venues/similar}}
        but it costs one API call everytime.
    \item twitter: get some code using the
        \href{https://github.com/geduldig/TwitterAPI}{TwitterAPI} python
        module.
    \item time pattern: mostly done, need real data to test relevance
\end{itemize}

\section*{Follow up}
\begin{itemize}
	\item \texttt{xaa}: running on triton
	\item others: postponed to tomorrow
	\item scraping: postponed
	\item twitter: still need to obtain API key
	\item mapping: postponed
	\item heatmap: WIP
\end{itemize}

\section*{Activity}
\begin{verbatim}
start working on html heatmap
A    leaflet/map.html
A    leaflet/vizu.js
M    utils.py
put all API key in the same file
M    .gitignore
M    AskFourquare.py
M    grab_photos.py
save errors instead of printing them
M    VenueIdCrawler.py
M    read_foursquare.py
don't discard check in without venue id
M    read_foursquare.py
allow setting an inital cache of url>id mapping
M    VenueIdCrawler.py
write week log
A    diary/20140213.tex
a class that make request to 4SQ API regarding venue and categories
A    AskFourquare.py
\end{verbatim}
