\subsection{General Description of the Dataset}

Using the Flickr API, we downloaded metadata from every photos satisfying a
set of criteria: they contained at least one tag, they were located, they have
been uploaded after January 1\textsuperscript{st}, 2008 and they belonged to a
predefined rectangular region. Most of the work was done on a set of around
\numprint{780000} photos in the city of San Francisco, but we also got data in
a part California\footnote{from San José to Reno} and over the whole United
States.

More precisely, in addition to tags and location, we know when each photos was
taken and uploaded, by which user and what title was given to it (the title
was not used except when it contained hashtag, that were converted to tags).
Thus a typical data point look like this:

\vspace{\baselineskip}
{\centering\begin{minipage}{0.7\linewidth}
  \begin{Verbatim}[frame=none, gobble=0]
loc     : [-122.392501, 37.77515],
taken   : "2008-03-24 14:55:40",
user_id : "37417902@N00",
tags    : ["sanfrancisco", "california", "bridge", "chinabasin"]
title   : "sf 4th st bridge 8"
  \end{Verbatim}
\end{minipage}\par}

\subsection{Uncertainty of the data}
\label{p:data}
\begin{itemize}
	\item User id are subject to caution since nothing prevent people to
 upload photos on behalf of others. It would require serious effort to
 detect it but one may expect it is rather uncommon. Moreover, the mere
 fact that the upload take place still denotes a relation between the
 user and the photos.
	\item While timestamp issued by mobile phones are likely to be correct,
 as their internal clock is synchronized by internet, this may not
 always be the case for dedicated cameras. More concerning than usual
 drift of low quality clock is the situation of tourists coming from
 different timezone. Yet as I could not think of any simple solution to
 that problem, I just ignored it and carried on.
	\item To ensure the quality of the localization, I restrict myself to
 photos whose precision is deemed \enquote{street level} by Flickr. The
 potential problem is that it would again cost an extra request to know
 whether this location was given by GPS (in which case the camera
 position is accurate) or by the user at upload time. In the latter
 case, in addition to the general imprecision of the method, it is
 ambiguous whether this location refer the place where the photo was
 shot or the position of the photo's subject\footnote{Think of a bridge
 taken from a nearby hill.}.
	\item Finally, without additional request, the tags obtained are those
 normalized by Flickr. This normalization is not bijective but it is
 assumed that two tags with the same normalized form were close in the
 first place.
\end{itemize}

Overall, these restrictions are not really problematic. Yet there is another
one that is not specific to a given field. Users have the possibility to
upload photos by batch and assign them common location and tags. In some case,
this could skew the corresponding distributions. Take the tag
\textsf{14thstreet} as an example. One user have uploaded more than
\numprint{3500} photos at one corner street during a marathon whereas only a
handful of others users have employed this tag, which is therefore not as
popular as the raw number would suggest. To alleviate this situation, I
performed a simple preprocessing step that I will describe later.

First, I duplicated the \enquote{tags} field of every photos. Then, for each
user $u$ and each tag $t$, I computed the distribution of photos tagged $t$ by
$u$ and removed the tags from the photos that appeared more than $T=120$ times
in the same place (the same cell of the $200\time 200$ discrete grid) in the same
time (2 weeks interval). With such threshold, it removed around 20\% of all
tags and it somewhat modified the list of top tag but with no clear pattern.
But tags with very low entropy like \textsf{14thstreet} did not appear
anymore because they lost most of their support. A better way to deal with
that issue could be to weight tags by the number of their users but it would
computationally more expensive.
