\begin{abstract}
Provide a short description of the project (problem studied, contributions, findings).
\end{abstract}

\section{Introduction}

A common way of organizing information on websites it to rely on tags provided
by users. Although these words are chosen freely, we do not expect them to be
arbitrary and thus hope to be able to extract limited semantics from them. In
this project, we focus on tags associated with geolocated photos extracted
from
Flickr\footnote{\href{https://secure.flickr.com/}{http://www.flickr.com/}}.
Using this crowdsourced set of (tags, location) pairs, we investigate three
problems:
\begin{itemize}
	\item Given a tag, find the places in a city where it is significantly
		concentrated.
	\item Conversely, given a location, find the tags that best describe it
		compared with other locations of similar scale.
	\item Finally, find the places in the city that seems to generate the
		most interest.
\end{itemize}

In the first case, it could be applied in a touristic context. When arriving in a
new city, a person interested in \textsf{baseball} or \textsf{streetart} could
find relevant places according to the experience of inhabitants and previous
visitors. The second answer could be used by Flickr to suggest relevant tags
when users upload photos. Consequently, more sensibly tagged photos allow more
relevant search result and improve the website user experience. The last could
for instance the first step of an automatic travel guide that select point of
interest in a city or a region.

Other applications may include inferring missing information (like location or
time of the day) from the tags or…

What are the contributions of this project?

\section{Setting}
\label{sec:setting}

Provide information that will be necessary for a reader to understand your contributions.

\subsection{General Description of the Dataset}

Using the Flickr API, we downloaded metadata from every photos satisfying a
set of criteria: they contained at least one tag, they were located, they have
been uploaded after January 1\textsuperscript{st}, 2008 and they belonged to a
predefined rectangular region. Most of the work was done on a set of around
\numprint{780000} photos in the city of San Francisco, but we also got data in
a part California\footnote{from San José to Reno} and over the whole United
States.

More precisely, in addition to tags and location, we know when each photos was
taken and uploaded, by which user and what title was given to it (the title
was not used except when it contained hashtag, that were converted to tags).
Thus a typical data point look like this:

\vspace{\baselineskip}
{\centering\begin{minipage}{0.7\linewidth}
  \begin{Verbatim}[frame=none, gobble=0]
loc     : [-122.392501, 37.77515],
taken   : "2008-03-24 14:55:40",
user_id : "37417902@N00",
tags    : ["sanfrancisco", "california", "bridge", "chinabasin"]
title   : "sf 4th st bridge 8"
  \end{Verbatim}
\end{minipage}\par}

\input{data}

\subsection{Statistical exploration}
\input{stats}
\section{Algorithms}
\label{sec:algorithms}

Define the algorithms you employ for the purposes of the project.

\section{Experimental Evaluation}

Here you report your findings from running your algorithms
(Section~\ref{sec:algorithms}) on your data (Section~\ref{sec:setting}).

\section{Conclusion \& Future Work}

\balance{}
\input{future}
